Efficient implementation of kernel filtering

### 2007-06-29 article/Article.tex
spell check
darcs-hash:20070629054141-fafb9-f6a798c062900ad4c9f5790a2f7d65cd1425f14f.gz

\subsection{Arbitrary structuring elements}
\label{sect:MMmovingHist}
The method described in \cite{Vandroogenbroeck96.3} relies on the
simple concept of an updatable histogram, and is often described as a
``moving histogram'' approach. A histogram is computed for a kernel
located at the first voxel. The histogram at the neighboring voxel can
then be computed by including newly included voxels and removing newly
excluded voxels. The list of included and excluded voxels
corresponding to movement in any direction can be computed when the
structuring element is created, and the direction with the smallest
number of changes should be selected as the direction for sweeping the
kernel across the image. The erosion or dilation at each location is
computed by selecting the minimum or maximum from the histogram. This
approach is very efficient when 8 or 16 bit pixels are used because
the histogram can be represented as an array, with place holders
tracking the current maximum or minimum increasing performance. More
sophisticated histogram representations are necessary for larger pixel
types. Our implementation uses c++ maps, which is an extension to the
original paper.

@@

\section{ITK implementation}
The filters discusses in this article are contained in 3 packages --
{\em consolidatedMorphology}, {\em fastRankMean} and {\em
boxConvolution}. The most recent versions of these packages can be
obtained from {\bf link to Gaetan's darcs repo}. All of the packages
include multithreaded filters and include many examples.

@@

\subsection{Rectangular convolution -- boxConvolution}
The {\em boxConvolution} uses the accumulation method described in
Section \ref{sect:meanVar} to implement rectangular mean and variance
computations. The filters implement different boundary conditions to
{\em itkMeanImageFilter}, with the mean of the kernel inside the image
being computed. The filters in this package are multithreaded and deal
with arbitary dimensions. The current filters do not support the mode
of operation used in face recognition application in which an
accumulation image is repeatedly ``queried'' for mean values of
various sized kernels. However introducing such a capability is
relatively easy.

>>>>

\subsection{Arbitrary structuring elements}
\label{sect:MMmovingHist}
The method described in \cite{Vandroogenbroeck96.3} relies on the
simple concept of an up-datable histogram, and is often described as a
``moving histogram'' approach. A histogram is computed for a kernel
located at the first voxel. The histogram at the neighboring voxel can
then be computed by including newly included voxels and removing newly
excluded voxels. The list of included and excluded voxels
corresponding to movement in any direction can be computed when the
structuring element is created, and the direction with the smallest
number of changes should be selected as the direction for sweeping the
kernel across the image. The erosion or dilation at each location is
computed by selecting the minimum or maximum from the histogram. This
approach is very efficient when 8 or 16 bit pixels are used because
the histogram can be represented as an array, with place holders
tracking the current maximum or minimum increasing performance. More
sophisticated histogram representations are necessary for larger pixel
types. Our implementation uses c++ maps, which is an extension to the
original paper.

@@

\section{ITK implementation}
The filters discusses in this article are contained in 3 packages --
{\em consolidatedMorphology}, {\em fastRankMean} and {\em
boxConvolution}. The most recent versions of these packages can be
obtained from {\bf link to Gaetan's darcs repo}. All of the packages
include multithreaded filters and include many examples. Unless
indicated otherwise, all filters will behave basically the same way as
other kernel filters, requiring either a radius or a neighborhood to
be specified.

@@

\subsection{Rectangular convolution -- boxConvolution}
The {\em boxConvolution} uses the accumulation method described in
Section \ref{sect:meanVar} to implement rectangular mean and variance
computations. The filters implement different boundary conditions to
{\em itkMeanImageFilter}, with the mean of the kernel inside the image
being computed. The filters in this package are multithreaded and deal
with arbitrary dimensions. The current filters do not support the mode
of operation used in face recognition application in which an
accumulation image is repeatedly ``queried'' for mean values of
various sized kernels. However introducing such a capability is
relatively easy.
